Paper_analyses

### 2021-08-03 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

pupil_arousal_findings$pupil_from_ar_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ valence_c* arousal_c | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num< 500 & 
                                      arousal_outler == FALSE))

# relgrad <- with(pupil_arousal_findings$pupil_from_ar_vale@optinfo$derivs,solve(Hessian,gradient))
# max(abs(relgrad))0.0002044252

@@

interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_val_gaze , pred = arousal_c, modx = valence_c)

@@

interactions::interact_plot(pupil_arousal_findings$pupil_resid_from_ar_vale , pred = arousal_c, modx = valence_c)

@@

@@

tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimIAPS, ssid,valence_self)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(stimIAPS, arousal, color = valence_self))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange')

tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimIAPS, ssid,valence_self)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(stimIAPS, abs(valence), color = valence_self))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange')

tmp.df4_full_stim_downs_jun2021_60bins%>%
  group_by(stimIAPS, ssid,ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(stimIAPS, abs(valence), color = ground_valence))+
  # geom_point()+
  stat_summary(funy = mean, geom = 'pointrange')
```
```{r}
# create the new arousal corrected within positive/negative - neutral
tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground_z <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal,
                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground / 
                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_sd_arousal, 
                                                                           tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ sd(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean, na.rm = TRUE)))

@@

>>>>

db_full4new_stim_screen_pupil_nopract$ssid<- as.factor(as.character(db_full4new_stim_screen_pupil_nopract$ssid))

pupil_arousal_findings$pupil_from_ar_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid)+
                                                    (0+ valence_c* arousal_c | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num< 500 & 
                                      arousal_outler == FALSE))
unique(db_full4new_stim_screen_pupil_nopract$tNo)

unique(db_full4new_stim_screen_pupil_nopract$ssid)
relgrad <- with(pupil_arousal_findings$pupil_from_ar_vale@optinfo$derivs,solve(Hessian,gradient))
max(abs(relgrad)) #0.0002044252

@@

plots_paper$interaction_ar_vl <- interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale , pred = arousal_c, modx = valence_c, plot.points = TRUE)

@@

plots_paper<- list()
plots_paper$interaction_ar_vl <- interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale, pred = arousal_c, modx = valence_c)

@@

plots_paper$interaction_ar_vl+p$graphstyle
```
interaction plot

```{r}
sf = 1 # scaling factor to make it easier to change sizes of everything, in which case change here

p$graphstyle_int <-  theme(#base plot theme

  # axis lines
  axis.line.y = element_line(color="black", size = 1.5),
  axis.line.x = element_line(color="black", size = 1,5),

  # panel
  panel.grid.major = element_blank(),
  panel.background = element_blank(),
  # panel.background = element_rect(fill="transparent"),
  # panel.border = element_rect(fill="transparent"),
  # strip shades (reco rectagles)
   # strip.background = element_blank(),

  #legend.text = element_text(size = 10*sf),
  # legend.title=element_blank(),
  #legend.text = element_blank(),
  #axis.ticks = element_blank(),
)

plots_paper$interaction_ar_vl<- plots_paper$interaction_ar_vl +
  theme_classic()+
  p$graphstyle_int+
  xlab("Arousal (z)")+
  ylab("Pupil change (z)")+
  scale_y_continuous(breaks = c(-1,0,1))

plots_paper$interaction_ar_vl<- plots_paper$interaction_ar_vl+   scale_y_continuous(breaks = c(-2,-1,0,1), limits = c(-2,1))

 plots_paper$interaction_ar_vl +
   theme_classic()+
   p$graphstyle_int

plots_paper[["interaction_ar_vl"]][["data"]]%>%
  ggplot(aes(arousal_c, pup_basCor, linetype = modx_group))+
  stat_summary(aes(color = valence_c), geom = 'line', size = 2)+
  p$graphstyle_int
```

@@

<!-- tmp.df4_full_stim_downs_jun2021_60bins%>% -->
<!--   group_by(stimIAPS, ssid,valence_self)%>% -->
<!--   summarise_if(is.numeric, mean, na.rm = TRUE)%>% -->
<!--   ggplot(aes(stimIAPS, arousal, color = valence_self))+ -->
<!--   # geom_point()+ -->
<!--   stat_summary(funy = mean, geom = 'pointrange') -->

<!-- tmp.df4_full_stim_downs_jun2021_60bins%>% -->
<!--   group_by(stimIAPS, ssid,valence_self)%>% -->
<!--   summarise_if(is.numeric, mean, na.rm = TRUE)%>% -->
<!--   ggplot(aes(stimIAPS, abs(valence), color = valence_self))+ -->
<!--   # geom_point()+ -->
<!--   stat_summary(funy = mean, geom = 'pointrange') -->

<!-- tmp.df4_full_stim_downs_jun2021_60bins%>% -->
<!--   group_by(stimIAPS, ssid,ground_valence)%>% -->
<!--   summarise_if(is.numeric, mean, na.rm = TRUE)%>% -->
<!--   ggplot(aes(stimIAPS, abs(valence), color = ground_valence))+ -->
<!--   # geom_point()+ -->
<!--   stat_summary(funy = mean, geom = 'pointrange') -->

```{r}
# create the new arousal corrected within positive/negative - neutral
tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground_z <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal,
                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground / 
                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_sd_arousal, 
                                                                           tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ sd(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean, na.rm = TRUE)))

@@

use the same dataas timecourse to plot aggregated analyses
aggregate arousal plot
```{r}

db_full4new_stim_screen_pupil_nopract$ground_valence_2<-
  cut(db_full4new_stim_screen_pupil_nopract$ValenceMean, c(0,4,5,9), 
                                                              labels = c("negative", "neutral", "positive"))

db_full4new_stim_screen_pupil_nopract$sample_valence_lab2<-
  cut(db_full4new_stim_screen_pupil_nopract$ValenceMeanThisSample, c(-10,-3,3,10), 
                                                              labels = c("negative", "neutral", "positive"))

db_full4new_stim_screen_pupil_nopract$ground_arousal_2<-
  cut(db_full4new_stim_screen_pupil_nopract$ArousalMean, c(0,4,5,9), 
                                                              labels = c("low", "mid", "high"))

db_full4new_stim_screen_pupil_nopract$sample_arousal_lab2<-
  cut(db_full4new_stim_screen_pupil_nopract$ArousalMeanThisSample, c(-10,-3,3,10), 
                                                              labels = c("low", "mid", "high"))

subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num<500 & 
                                      arousal_outler == FALSE)%>%
  ggplot(aes(sample_valence_lab2, arousal))+
  geom_point()+
  stat_summary(geom = 'pointrange')

subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num<500 & 
                                      arousal_outler == FALSE)%>%
  group_by(ssid, mediansplit_ground_valence, mediansplit_ground_arousal)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_valence, pup_resid_lm, color = mediansplit_ground_arousal ))+
  # geom_point()+
  stat_summary(geom = 'pointrange')

subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num<500 & 
                                      arousal_outler == FALSE)%>%
  group_by(ssid, mediansplit_ground_valence, mediansplit_ground_arousal)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_valence, pup_resid_lm, color = mediansplit_ground_arousal ))+
  # geom_point()+
  stat_summary(geom = 'pointrange')
